# Documentation - bookdown-styled

First, choose _New Project_ and _New Directiory_. 

Second, choose _Book Project using bookdown_ and pick a name as well as your preferred directory. RStudio will automatically set up the Rproj as well as the folder skeleton. 

Third, tie the existing project with Git through the `usethis` package. It will re-organise the existing project folder and prepare the Git integration. 
```{r eval=FALSE}
> usethis::use_git()

✔ Setting active project to '/Users/sushicat/Dropbox/R_Me/R_DE'
✔ Initialising Git repo
✔ Adding '.Rhistory', '.RData', '.Rproj.user' to '.gitignore'
There are 15 uncommitted files:
* '_bookdown.yml'
* '_output.yml'
* '.gitignore'
* '01-intro.Rmd'
* '02-literature.Rmd'
* '03-method.Rmd'
* '04-application.Rmd'
* '05-summary.Rmd'
* '06-references.Rmd'
* 'book.bib'
* 'index.Rmd'
* 'preamble.tex'
* 'R_DE.Rproj'
* 'README.md'
* 'style.css'
Is it ok to commit them?

1: Not now
2: For sure
3: No way

Selection: 2
✔ Adding files
✔ Commit with message 'Initial commit'
● A restart of RStudio is required to activate the Git pane
Restart now?

1: Not now
2: Yup
3: Absolutely not

Selection: 2
```

Fourth, create a GitHub repo through the `usethis` package and if the project name is available on the owner's repos. When facing git protocol, choose `https`. 
```{r eval=FALSE}
> usethis::use_github()

✔ Setting active project to '/Users/sushicat/Dropbox/R_Me/R_DE'
✔ Checking that current branch is 'master'
Which git protocol to use? (enter 0 to exit) 

1: ssh   <-- presumes that you have set up ssh keys
2: https <-- choose this if you don't have ssh keys (or don't know if you do)

Selection: 2
● Tip: To suppress this menu in future, put
  `options(usethis.protocol = "https")`
  in your script or in a user- or project-level startup file, '.Rprofile'.
  Call `usethis::edit_r_profile()` to open it for editing.
● Check title and description
  Name:        Bradford
  Description: 
Are title and description ok?

1: Yeah
2: Not now
3: Absolutely not

Selection: 1
✔ Creating GitHub repository
✔ Setting remote 'origin' to 'https://github.com/dataning/R_DE.git'
✔ Pushing 'master' branch to GitHub and setting remote tracking branch
✔ Opening URL 'https://github.com/dataning/R_DE'
```

Fifth, create and save a random R.script in the current project. The commit and push the change of the project to your GitHub repo. You can go to your GitHub repo and check if the R script has been added. This should tell you whether your Rproj and GitHub Repo are fully synced/integrated. 

Sixth, go to Netlify and deploy your GitHub repo on Netlify. This will give you the ability to perform continuous deployment as well as deployment to custom domain.  

There's a number of information you need to select or put down in Netlify.
- Your Rpoj's GitHub repo name
- `_book`
